### 2013-08-02 main.tex
use chapters
copy *& paste everything

\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\W}{\mathcal{W}}

@@

\pagenumbering{Roman}
\tableofcontents
\listoffigures
\listoftables
 \chapter*{Acknowledgements}
 \begin{abstract} abstract
\end{abstract}
\pagenumbering{arabic}

@@

\end{document}

>>>>

\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\renewcommand{\eqref}[1]{Equation~(\ref{#1})}
\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\newcommand{\W}{\mathcal{W}}

\newcommand{\given}{\, | \,}
\newcommand{\B}[1]{\textbf{#1}}

@@

\pagenumbering{Roman}

\tableofcontents

%\listoffigures
%\listoftables
\chapter*{Acknowledgements}

\begin{abstract} abstract
\end{abstract}

\pagenumbering{arabic}

\chapter{Information Theoretic Clustering for Object Class Discovey}
\include{itm/paper}

\chapter{Weakly Supervised Object segmentation via Multiple Instance Learning}
\include{partial_supervision/paper}
\include{mil/paper}

\chapter{Concepts and Implementation of Conditional Random Field-based Semantic Segmentation}

\include{pystruct/paper}

\chapter{Efficient Exact Learning of Loopy CRFs}

@@

\chapter{Hierarchical Latent Variable Models for Semantic Segmentation}

\bibliography{main}
\end{document}
